An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-09-01 EconGrowth2.Rnw
Example text for GitHub testing.

@@

Benes, J., Chauvet, M., Kamenik, O., Kumhof, M., Laxton, D., Mursula, S., and Selody, J. (2012). The Future of Oil: Geology versus Technology. IMF Working Papers, I12/109, 1–33.

@@

Duffy, J., and Papageorgiou, C. (2000). A Cross-Country Empirical Investigation of the Aggregate Production Function Specification. Journal of Economic Growth, 5(1), 87–120. doi:10.1023/A:1009830421147

Fröling, M. (2011). Energy use, population and growth, 1800–1970. Journal of Population Economics, 24(3), 1133–1163.

Galor, O., and Weil, D. N. (2000). Population,Technology, and Growth: From Malthusian Stagnation to the Demographic Transition and Beyond. American Economic Review, 90(4), 806–828.

Jones, C. (2001). Was an industrial revolution inevitable? Economic growth over the very long run. Advances in Macroeconomics, 1(2), 1–43.

Kemfert, C. (1998). Estimated substitution elasticities of a nested CES production function approach for Germany. Energy Economics, 20(3), 249–264.

@@

Lecca, P., Swales, K., and Turner, K. (2011). An investigation of issues relating to where energy should enter the production function. Economic Modelling, 28(6), 2832–2841.

>>>>

Matt added this text to debug his GitHub account.

@@

@@

@@
